A semantics of core AUTOSAR

### 2016-04-25 paper/paper.tex
Starting to merge the updated semantics into paper/semantics.tex

Some further static model information will also be referenced by the transition rules. We refer to the \emph{connectors} of a model using a binary relation $\Rightarrow$ on addresses, defined as
$$
	\adr{E:$U_1$:$I_1$} \Rightarrow \adr{E:$U_2$:$I_2$} \;\;\text{for all elements $E$ of port $U_2$}
$$
if there is a connector in the model from provided sender-receiver port $U_1$ of component $I_1$ to required port $U_2$ of component $I_2$; and
$$
	\adr{O:$U_1$:$I_1$} \Rightarrow \adr{O:$U_2$:$I_2$} \;\;\text{for all operations $O$ of port $U_1$}
$$
if there is a connector in the model from required client-server port $U_1$ of component $I_1$ to provided port $U_2$ of component $I_2$.

>>>>

Some further static model information will also be referenced by the transition rules. We refer to the \emph{connectors} of a model using a binary relation $\Rightarrow$ on addresses, defined as
$$
	\Tconnect{\adr{E:$U_1$:$I_1$}}{\adr{E:$U_2$:$I_2$}} \;\;\text{for all elements $E$ of port $U_2$}
$$
if there is a connector in the model from provided sender-receiver port $U_1$ of component $I_1$ to required port $U_2$ of component $I_2$; and
$$
	\Tconnect{\adr{O:$U_1$:$I_1$}}{\adr{O:$U_2$:$I_2$}} \;\;\text{for all operations $O$ of port $U_1$}
$$
if there is a connector in the model from required client-server port $U_1$ of component $I_1$ to provided port $U_2$ of component $I_2$.
